### 2020-06-30 2020/wada/adaptive_domain_adaptation.tex
correct some errors

If we the original version of the residual adapter, with the same assumption in the regularization of the adapter, the bound of the risk of translating out-of-domain is only A (the bound of loss function). By using adaptive version, we reduce A by factor $\frac{p_0}{\epsilon^k_{insep}+\gamma}$ which is high if we choose $p_0$ is high enough, the domains are distant and the classifier is good enough.

>>>>

If we the original version of the residual adapter, with the same assumption in the regularization of the adapter, the bound of the risk of translating out-of-domain is only A (the bound of loss function). By using adaptive version, we reduce A by factor $\frac{p_0}{\epsilon^k_{insep}+\gamma}$ which is high if we choose $p_0$ is high enough, the domains are distant in the fixed representation space and the classifier is good enough.
